outline

### 2019-11-27 Rmd/introduction.Rmd
added citation
added intro text; added more bib citations

- big data
- new areas of application of statistical methods - social media
- need for mentoring 
- need for students to work with real data
- motivate statistical analysis by real world research questions

>>>>

- big data
- new areas of application of statistical methods - social media
- need for mentoring 
- need for students to work with real data
- motivate statistical analysis and statistics research by real world scientific research questions (Box 1976)

@nolan2010computing

The need to analyze unprecedentedly large volumes of information combined with 
the development of faster and more powerful computers has fueled advances in 
data science methods for big data. We present below a framework for mentored 
undergraduate data science research and our findings from its initial 
implementation for two statistics students. We conclude with lessons learned 
and suggestions for those who wish to reproduce and refine our framework.

Social media data, including tweets from Twitter and posts from Facebook, are 
available through website application product interfaces (APIs). Twitter 
shares, via a streaming API, a sample of approximately one percent of all 
tweets during an API query time period. Researchers have studied tweets for a 
variety of purposes, including 
inference of relationships and social networks among users [@lin2011joint]; determination of 
authorship of specific tweets when multiple persons use a single account [@drob]; and 
study of rhetoric in recruiting political supporters [@pelled2018little,@wells2016trump].
